gij bent 2

### 2025-09-30 paper/paper.qmd
Add abstract

---
title: "gij bent 2"
author:
  - name: Anthe Sevenants
    email: anthe.sevenants@kuleuven.be
    orcid: 0000-0002-5055-770X
    affiliations:
      - name: KU Leuven
  - name: Julie Nijs
    email: julie.nijs@kuleuven.be
    orcid: 000-0002-7421-9887
    affiliations:
      - name: KU Leuven
format:
  html:
    toc: true
  docx:
    toc: false
  pdf:
    geometry:
      - top=20mm
      - left=20mm
      - right=20mm
      - bottom=20mm
      - heightrounded
editor: source
title-block-banner: true
bibliography: references.bib
toc: true
toc-depth: 4
toc-location: left
tbl-cap-location: bottom
fig-cap-location: bottom
number-sections: true
#reference-location: margin
csl: chicago-author-date.csl
df-print: kable
abstract: |
  TODO
execute:
  echo: false
---

>>>>

---
title: "gij bent 2"
author:
  - name: Anthe Sevenants
    email: anthe.sevenants@kuleuven.be
    orcid: 0000-0002-5055-770X
    affiliations:
      - name: KU Leuven
  - name: Julie Nijs
    email: julie.nijs@kuleuven.be
    orcid: 000-0002-7421-9887
    affiliations:
      - name: KU Leuven
format:
  html:
    toc: true
  docx:
    toc: false
  pdf:
    geometry:
      - top=20mm
      - left=20mm
      - right=20mm
      - bottom=20mm
      - heightrounded
editor: source
title-block-banner: true
bibliography: references.bib
toc: true
toc-depth: 4
toc-location: left
tbl-cap-location: bottom
fig-cap-location: bottom
number-sections: true
#reference-location: margin
csl: chicago-author-date.csl
df-print: kable
abstract: |
  Language change finds its origins in individual variation. Individual behaviour, however, is rarely taken into account in variationist studies. In this study, we look at innovative *gij bent* from Colloquial Belgian Dutch through a corpus of 16,968 tweets by 555 authors. With elastic net regression, we build a linguistic profile for each individual author: 51% of authors are more innovative than one would expect from their dialect area and gender, 49% are more conservative. When we plot these deviations regionally, we see a potential future horizontal diffusion pattern. Additionally, we find that influential tweet authors tend to be more innovative. Therefore, *gij bent* might currently be in the "early adopters" stage of diffusion. In general, our results show that a focus on the individual offers new perspectives which might remain hidden in traditional variationist analyses.
execute:
  echo: false
---
